%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Expert Engineer, Web Full Stack} % Job title
    {Sea Ltd.} % Organization
    {Singapore} % Location
    {Feb. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained multiple internal applications using Python (Django REST) and MySQL.}
        \item {Developed shared Python libraries, enhancing collaboration and efficiency across team projects.}
        \item {Successfully led a team in executing seamless data migration for a Finance product, handling millions of records for each primary model.}
        \item {Supported the migration of multiple projects to a more mature platform.}
        \item {Gate keeping 20+ Python Django projects within the team, oversee all the django-related technical decisions within the team.}
      \end{cvitems}
    }

  \cventry
    {Senior Engineer, Web Full Stack} % Job title
    {} % Organization
    {} % Location
    {Feb. 2020 - Jan. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained multiple internal applications using Python (Django) Javascript (AngularJs), and MySQL.}
        \item {Developed and maintained critical Finance systems, serving as a cornerstone for Finance-related management functions of the entire company.}
        \item {Orchestrated a team of 4 developers to integrate 4 products with the Approval Center, consolidating approval items for all managers.}
        \item {Led a team in the data migration of an IT product, ensuring the smooth transition of vast datasets and setting up a data migration workload, later applied to future migrations within the team.}
        \item {Implemented and optimized GitLab pipeline processes, fostering automation testing for increased efficiency.}
        \item {Created and sustained the HR Information System (HRIS), a core tool for HR to manage employee information, supporting various API integrations for streamlined data retrieval.}
        \item {Actively participated as an interviewer, contributing to the recruitment and selection process for the entire department.}
        \item {Proposed a field validation error standard based on JSONSchema validation, enhancing collaboration between Frontend and Backend during the development process.}
        \item {Mentored multiple new hires in the team in order for them to understand more on internal tooling and processes in order to be productive and able to contribute to development smoothly.}
      \end{cvitems}
    }

  \cventry
    {Engineer, Web Full Stack} % Job title
    {} % Organization
    {} % Location
    {Nov. 2017 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained multiple internal applications using Python (Django) Javascript (React \& AngularJs), and MySQL.}
        \item {Designed, developed, and maintained a comprehensive hiring system, including the Career Portal (https://career.sea.com), Head Hunter Portal (specialized for Head Hunter firms), and HR Interview Portal (facilitating interview scheduling for candidates).}
        \item {Developed and maintained the HR Information System (HRIS), a core tool for HR to manage employee information, supporting various API integrations for streamlined data retrieval.}
        \item {Worked with multiple interns to set up and launch a performance review system for the department, to help boost the efficiency of the entire review process.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Big-Data Fresher} % Job title
    {VNG Corp.} % Organization
    {Ho Chi Minh, Vietnam} % Location
    {Jul. 2016 - Jul. 2017} % Date(s)
    {
      \begin{cvitems}
        \item {Build monitoring-data website using Java Servlet Jetty Hapax, Apache Thrift.}
        \item {Build a core framework for analyzing game data using Big-Data tools: Apache Spark, Hive.}
        \item {Build a server for a poker game using Cubeia framework.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
